Poker Chips, Earthquakes, and Computation

### 2014-10-12 finaldraft.tex
Commented out Image
added global earthquakes to definitions and notation

Finally, we formalize the notion of $\emph{finite}$ and $\emph{infinite}$ boards, a distinction we will refer to extensively throughout this paper.

@@

@@

\begin{definition}
A $d$-tree is a graph composed of a parent node connected by edges to $d-1$ unique children nodes.Those children each have $d-1$ unique children and so on.  
\end{definition}
\begin{figure}[!h]
\label{4tree}
\centering
\includegraphics[width=0.4\linewidth]{4tree}
\caption{A 4-tree}
\end{figure}
We note that every node other than the original parent node has $d$ neighbors. In order to simplify our process we would like the graph to be regular and so we make the following definition. 
\begin{definition}
A joined $d$-tree is two $d$-trees connected at their parent nodes by an edge.
\end{definition}
\begin{figure}[!h]
\label{joined4tree}
\centering
\includegraphics[width=0.8\linewidth]{joined4tree}
\caption{A joined 4-tree}
\end{figure}

>>>>

We also formalize the notion of $\emph{finite}$ and $\emph{infinite}$ boards, a distinction we will refer to extensively throughout this paper.

@@

Finally, we use the above definitions to define global earthquakes, which will be defined only for finite boards. 
\begin{definition}
Given a finite board $b$, a global earthquake is given by applying one earthquake to every square in $b$ that initially has 4 or more chips.
\end{definition}

We will see in Section~\ref{Order of Redistribution} that the order in which earthquakes are applied does not matter, and thus global earthquakes are well-defined without the need for an ordering on the individual earthquakes. In order to avoid the case where there may be infinitely many squares with 4 or more chips, we only define global earthquakes for finite boards.

@@

\begin{definition}
A $d$-tree is a graph composed of a parent node connected by edges to $d-1$ unique children nodes.Those children each have $d-1$ unique children and so on.  
\end{definition}
%\begin{figure}[!h]
%\label{4tree}
%\centering
%\includegraphics[width=0.4\linewidth]{4tree}
%\caption{A 4-tree}
%\end{figure}
We note that every node other than the original parent node has $d$ neighbors. In order to simplify our process we would like the graph to be regular and so we make the following definition. 
\begin{definition}
A joined $d$-tree is two $d$-trees connected at their parent nodes by an edge.
\end{definition}
%\begin{figure}[!h]
%\label{joined4tree}
%\centering
%\includegraphics[width=0.8\linewidth]{joined4tree}
%\caption{A joined 4-tree}
%\end{figure}
